\section{Operational Procedures} \label{sec:docs}

\subsection{Operations Readiness Requirement}

The project team shall deliver a complete set of documented operational procedures and supporting technical documents needed to operate the LSST as a scientific facility to conduct a 10-year survey.

\subsection{Objectives:}

The objective of this Operational Requirement is to ensure that the procedures necessary for the operations and maintenance of the Rubin Observatory are documented and provided in a form that allows the operations team to conduct the 10-year planned survey. The documentation is to include but is not limited to:


\subsection{Criteria for Completeness}

The documentation is to include but is not limited to:

\begin{itemize}
	\item Process procedures describing user-level standard operations
	%new_hd
	The documentation for the Observing specialist as the main users of the observatory is under development in Confluence and can be found \href{https://rubinobs.atlassian.net/wiki/spaces/OST/overview | here] under \it{Training and Skills}
	
	\item Maintenance needs and procedures for all systems in use
	%new_hd
	The observatory has implemented a Computerized Maintenance Management System (CMMS). 
	It holds a growing number of the latest versions of repeatedly used maintenance procedures.
	
	\item A history of maintenance carried out during construction and commissioning
	%new_hd
	The CMMS allows for documenting the execution of maintenance activities and provides the history of all maintenance executions.

	\item System software documentation - including their operating versions, functionality, and interactions with other systems
	%new_hd
	
	\item The observatory feature-based scheduler algorithms and documentation for modification and refinement
	%new_hd
	The feature-based scheduler is realized as a Comandable SAL Component. Its code and documentation are stored in GitHub.
	
	\item A definition of initial delivered science data products (see previous sections)	
\end{itemize}

{\bf Note:} At the time of this update, the Project has recently set up a "Documentation Working Group".  This working group is responsible for defining the architecture of the delivered documentation repositories.

\subsection{Pre--Operations Interactions}

The final delivered documentation will be negotiated between the Rubin Construction Project and Rubin Operations.

\subsection{Artifacts for CCR}

See Criteria above.
