\section{Verification of Observatory System Specifications (LSE-30)}  \label{sec:oss}

\subsection{Construction Completeness Criteria}
The project team shall demonstrate that the integrated LSST systems (Camera, Telescope \& Site and Data Management subsystems) as well as the Education and Public Outreach (EPO) system have met the technical specifications enumerated in the LSST Observatory System Specifications (\citeds {LSE-30}).

\subsection{Objectives}

The main objective with this Operations Readiness Requirement is to verify the system specifications in the OSS (LSE-30) are proven and well documented..  The OSS is essentially the highest level document describing the basic LSST system technical architecture.  It contains sections derived from the OSS on the following broad topics:

\begin{itemize}
\item System Composition and Constraints

\item Common System Functions and Performance, including:

	\begin{itemize}
		\item System Control
		\item System Monitoring and Diagnostics
		\item System Maintenance
		\item System Availability
		\item System Time References
	\end{itemize}

\item Detailed Specifications:

	\begin{itemize}
		\item Science and Bulk Data
		\item Optical System
		\item System Throughput
		\item Camera System
		\item Photometric Calibration
		\item System Timing and Dynamics
	\end{itemize}
	
\item Education and Public Outreach

\end{itemize}

\subsection{Criteria for Completeness}
Compliance with this objective will follow the process as defined in the Verification and ValidationProcess document (LSE-160) and associated documentation.   All technical specifications in the OSS (LSE-30) and LSR (LSE-29) are expected be met at the end of construction.

\subsection{Pre--Operations Interaction}
None.  Unless there are non-compliance issues against the ORR requirements and specifications.

\subsection{Artifacts for Completion}

\begin{itemize}
 
	\item Verification matrix containing entries for all OSS requirements and specifications.  Methods, inspections, demonstration, analysis or test, shall be identified for every OSS requirement.  Final compliance status will be included.

	\item Analysis reports where the verification method has been identified as "test" or "analysis".
	\item Non-compliance reports.

\end{itemize}